RUPEE: A fast and accurate purely geometric protein structure search

### 2018-11-16 docs/plos_latex_template.tex
supporting information

All benchmark definitions can be found in the supplementary material.

@@

A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in the supplementary material. 
The same relative relationships hold with only small variations.

@@

>>>>

All benchmark definitions can be found in \nameref{S3_Benchmarks}.

@@

A figure similar to \figurename~\ref{fig:combined_scoring_ce} but using FATCAT for pairwise comparisons can be found in \nameref{S1_Fig}. 
The same relative relationships hold with only small variations.

@@

\section*{Supporting information}

\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Scoring from FATCAT pairwise alignments.}

\paragraph*{S2 Methods.}
\label{S2_Methods}
{\bf Run factors for shingles instead of descriptors.}

\paragraph*{S3 Benchmarks.}
\label{S3_Benchmarks}
{\bf Domains included in benchmarks used for evaluation.}
